---
title: "gt_eprrai"
author: "Ryoun Ukita"
date: '2022-10-29'
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Regression based on EPR and RAI

```{r}
library(countrycode)
library(tidyverse)
library(dplyr)
library(tidyr)
library(MASS)
library(ineq)
library(survival)
library(stringr)
library(glmnet)
library(Epi)
library(sem)
library(ivprobit)
library(rms)
library(lme4)
library(plsRglm)
library(modelsummary)
library(mvtnorm)

raimlg <- read.csv("~/ukita-ryoun953@g.ecc.u-tokyo.ac.jp - Google Drive/My Drive/GraduationThesis/RAI_MLG/RAI_MLG_feb2021.csv")

epr <- read.csv("~/ukita-ryoun953@g.ecc.u-tokyo.ac.jp - Google Drive/My Drive/GraduationThesis/EPR/pad+ucdpacd/data.csv")

gdp <- read.csv("~/ukita-ryoun953@g.ecc.u-tokyo.ac.jp - Google Drive/My Drive/GraduationThesis/GDP&pop/Penn.gdp_ver2.csv")

pop <- read.csv("~/ukita-ryoun953@g.ecc.u-tokyo.ac.jp - Google Drive/My Drive/GraduationThesis/GDP&pop/Penn.pop_ver2.csv")

bednarfederal <- read.csv("/Volumes/GoogleDrive-114345131165924653723/My Drive/GraduationThesis/TERRGO/bednarfederal.csv")

mcgarryfederal <- read.csv("/Volumes/GoogleDrive-114345131165924653723/My Drive/GraduationThesis/TERRGO/mcgarryfederal.csv")

```

## filtering contries which exist both datasets 
```{r}
eprserbia <- epr %>% filter(countries_gwid == 340)
raiepr_match <- intersect(raimlg$cowcode, epr$countries_gwid)

raiinepr <- raimlg %>% dplyr::filter(cowcode %in% raiepr_match)
eprinrai <- epr %>% filter(countries_gwid %in% raiepr_match & isactive == 1)

write.csv(raiinepr, file = "~/ukita-ryoun953@g.ecc.u-tokyo.ac.jp - Google Drive/My Drive/GraduationThesis/RAI_MLG/raiinepr.csv", row.names = FALSE)
write.csv(eprinrai, file = "~/ukita-ryoun953@g.ecc.u-tokyo.ac.jp - Google Drive/My Drive/GraduationThesis/RAI_MLG/eprinrai.csv", row.names = FALSE)
write.csv(eprserbia, file = "~/ukita-ryoun953@g.ecc.u-tokyo.ac.jp - Google Drive/My Drive/GraduationThesis/RAI_MLG/eprserbia.csv", row.names = FALSE)
```

## filling the identifiers in manually

##
```{r}
eprinrai_formatch <- read.csv("/Volumes/GoogleDrive-114345131165924653723/My Drive/GraduationThesis/RAI_MLG/eprinrai_ver2.csv")
raiinepr_formatch <- read.csv("/Volumes/GoogleDrive-114345131165924653723/My Drive/GraduationThesis/RAI_MLG/raiinepr_ver2.csv")
eprserbia_formatch <- read.csv("/Volumes/GoogleDrive-114345131165924653723/My Drive/GraduationThesis/RAI_MLG/eprserbia_ver2.csv")

eprserbia_formatch$rai_regionid <- as.character(eprserbia_formatch$rai_regionid)

zero <- as.integer(0)
eprinrai_formatch <- eprinrai_formatch %>%
  bind_rows(eprserbia_formatch) %>%
  arrange(gwgroupid, year) %>%
  filter(isactive == 1 & statusid != 5 & statusid != 1 & statusid != 2 & isrelevant == 1) %>% 
  separate_rows(rai_regionid, sep = ";")

eprinrai_formatch <- eprinrai_formatch %>%
  mutate(regaut = coalesce(regaut, zero)) %>%
  mutate(rai_regionid = coalesce(rai_regionid, as.character("S")))

raiinepr_formatch$regionid <- as.character(raiinepr_formatch$regionid)

raiinepr_formatch_standard <-  raiinepr_formatch %>%
  filter(tier == 1 & type == "S") %>%
  group_by(cowcode, year) %>%
  filter(RAI == max(RAI), popweight == max(popweight)) %>%
  ungroup()

eprrai_standard <- eprinrai_formatch %>%
  filter(rai_regionid == "S") %>%
  inner_join(raiinepr_formatch_standard, by = c("countries_gwid" = "cowcode", "rai_regionid" = "type", "year")) %>%
  mutate(type = rai_regionid,
         rai_regionid = regionid)

eprrai_asym <- eprinrai_formatch %>%
  filter(rai_regionid != "S") %>%
  inner_join(raiinepr_formatch, by = c("rai_regionid" = "regionid", "year"))

eprrai <- bind_rows(eprrai_standard, eprrai_asym) 
eprrai <- eprrai %>%
  dplyr::select(-c(173, 159:171))
```

## Filtering and mutating variables, joined by GDP and Population
```{r}
eprrai <- eprrai %>%
  dplyr::select(countryname, countries_gwid, year, groupname, gwgroupid, regaut, isactive, isrelevant, groupsize, status_egip, status_pwrrank, excl_groups_count, rlvt_groups_count, incidence_flag, incidence_terr_flag, onset_do_flag, onset_do_terr_flag, onset_ko_flag, onset_ko_terr_flag, warhist, peaceyears, rai_regionid, metro, c(125:159)) %>%
  mutate(squared_groupsize = (groupsize)^2,
         postwar = ifelse(warhist >= 1, 1, 0)
         )

gdp <- gdp %>%
  mutate(countries_gwid = countrycode(RegionCode, origin = 'iso3c', destination = 'cown', custom_match = c('SRB' = '340','SCG' = '345'))) %>%
  dplyr::select(countries_gwid, YearCode, AggValue) %>%
  rename(year = YearCode, gdp = AggValue) %>%
  arrange(countries_gwid, year) %>%
  group_by(countries_gwid) %>%
  mutate(lagged_gdp = lag(gdp)) %>%
  mutate(lgdp = log(lagged_gdp+1)) %>%
  ungroup()

pop <- pop %>%
  mutate(countries_gwid = countrycode(RegionCode, origin = 'iso3c', destination = 'cown', custom_match = c('SRB' = '340','SCG' = '345'))) %>%
  dplyr::select(countries_gwid, YearCode, AggValue) %>%
  rename(year = YearCode, pop = AggValue) %>%
  arrange(countries_gwid, year) %>%
  mutate(lpop = log(pop+1))

eprrai$countries_gwid <- as.character(eprrai$countries_gwid)

eprrai <- eprrai %>%
  left_join(gdp, by = c("countries_gwid", "year" ) ) %>%
  left_join(pop, by = c("countries_gwid", "year" ) )

summary(eprrai)
```


## Add two variables about Federation
```{r}
federalchange <- c("Belgium", "Malaysia", "Venezuela", "South Africa")
eprrai_federalchange <- eprrai %>%
  filter(countryname %in% federalchange) %>%
  left_join(mcgarryfederal, by = c("countryname", "year") ) %>%
  left_join(bednarfederal, by = c("countryname", "year") )

eprrai_federalnochange <- eprrai %>%
  filter(!(countryname %in% federalchange)) %>%
  left_join(mcgarryfederal, by = c("countryname")) %>%
  left_join(bednarfederal, by = c("countryname") ) %>%
  dplyr::select(-year) %>%
  rename(year = year.x)

eprrai <- bind_rows(eprrai_federalchange, eprrai_federalnochange)
eprrai <- eprrai %>%
  mutate(bednar_federal = coalesce(bednar_federal, zero),
         mcgarry_federal = coalesce(mcgarry_federal, zero)) %>%
  group_by(countries_gwid, year) %>%
  mutate(regaut_groups_count = length(unique(gwgroupid[regaut == 1])),
         noaut_groups_count = length(unique(gwgroupid[regaut == 0])),
         ongoing = case_when(
           length(unique(gwgroupid[incidence_flag == 1])) == 1 & incidence_flag == 1 ~ 0,
           length(unique(gwgroupid[incidence_flag == 1])) == 1 & incidence_flag == 0 ~ 0,
           length(unique(gwgroupid[incidence_flag == 1])) > 1 ~ 1,
           length(unique(gwgroupid[incidence_flag == 1])) == 0 ~ 0
         )) %>%
  ungroup()

summary(eprrai)
```

## Focusing on the regions with the maximum RAI where the ethnic group rules themself
```{r}
eprrai_max <- eprrai %>%
  filter((incidence_terr_flag == 0 & onset_ko_terr_flag == 0)| onset_ko_terr_flag == 1, regaut_groups_count + noaut_groups_count != 1, ) %>%
  dplyr::select(countries_gwid, countryname, year, gwgroupid, groupname, onset_ko_terr_flag, onset_do_terr_flag, regaut, status_egip, peaceyears, postwar, ongoing, excl_groups_count, bednar_federal, groupsize, squared_groupsize, lgdp, lpop, tier, type, metro, popweight, regaut_groups_count, noaut_groups_count, instdepth, policyautonomy, fiscalautonomy, borrowautonomy, representation, lawmaking, executivecontrol, fiscalcontrol, borrowcontrol, constitutional, selfrule, RAI) %>%
  mutate(noaut = ifelse(regaut == 1, 0, 1)) %>%
  arrange(countries_gwid, year, gwgroupid, RAI) %>%
  group_by(countries_gwid, year, gwgroupid) %>%
  filter(tier == min(tier)) %>%
  ungroup() %>%
  group_by(countries_gwid, year, gwgroupid) %>%
  filter(RAI == max(RAI)) %>%
  ungroup() %>%
  group_by(countries_gwid, year, gwgroupid) %>%
  filter(popweight == max(popweight)) %>%
  ungroup()

options(max.print = 50) # add the factor variables indicating above/below/equivalent to the standard regions
eprrai_max <- eprrai_max %>%
  arrange(countries_gwid, year, gwgroupid) %>%
  group_by(countries_gwid, year) %>%
  mutate(nstandard = length(gwgroupid[type == "S"])) %>%
  mutate(status_excl = ifelse(status_egip == 0, 1, 0),
         asym_high = ifelse(regaut == 0, 0,ifelse(selfrule > selfrule[type == "S"], 1, 0)),
         asym_low = ifelse(regaut == 0, 0,ifelse(selfrule < selfrule[type == "S"], 1, 0)),
         asym_same = ifelse(regaut == 0, 0,ifelse(selfrule == selfrule[type == "S"], 1, 0)),
         instdepth_diff = abs(instdepth - max(instdepth)),
         policyautonomy_diff = abs(policyautonomy - max(policyautonomy)),
         borrowautonomy_diff = abs(borrowautonomy - max(borrowautonomy)),
         fiscalautonomy_diff = abs(fiscalautonomy - max(fiscalautonomy)),
         representation_diff = abs(representation - max(representation)),
         ethnicselfrule = ifelse(regaut == 0, 0, selfrule),
         selfrule_diff = abs(ethnicselfrule - max(ethnicselfrule))) %>%
  ungroup()

eprrai_max <- eprrai_max %>%
  mutate(political_diff = policyautonomy_diff + representation_diff,
         fiscal_diff = borrowautonomy_diff + fiscalautonomy_diff)


```


## Cross tables
```{r}
diff_type <- eprrai_max %>% 
  group_by(selfrule_diff, type) %>% 
  tally %>% 
  spread(type, n) %>%
  rename(Autonomous = A,
         Dependent = D,
         Standard = S,
         Asymmetric = Y) %>%
  replace_na(replace = list(Autonomous = 0,
         Dependent = 0,
         Standard = 0,
         Asymmetric = 0)) %>%
  ungroup() %>%
  gt() %>%
  tab_options(table.width = pct(50),
              column_labels.border.top.width = 2, 
          column_labels.border.top.color = "black", 
          column_labels.border.bottom.width = 1, 
          column_labels.border.bottom.color = "black",
              table.border.top.width = 2,
              table_body.border.top.color = "black",
              table.border.bottom.width = 2,
              table_body.border.bottom.color = "black")

gt::gtsave(diff_type, "/Volumes/GoogleDrive-114345131165924653723/MyDrive/GraduationThesis/RAI_MLG/diff_freq.png")

```


## Replication of Cederman(2015) using data from 1950-2018 which countries exist in RAI dataset
Thus, there is no data for Soviet Union and Yugoslavia (~1992).
```{r}
model_cederman <- glm(onset_do_terr_flag ~
                           status_egip +
                           regaut +
                           regaut:status_egip +
                           postwar +
                           regaut:postwar +
                           groupsize +
                           squared_groupsize +
                           ongoing +
                           peaceyears +
                           bednar_federal +
                           lpop +
                           lgdp +
                           excl_groups_count,
                      data = eprrai_max,
                      family = binomial(link = "logit"))
modelsummary(model_cederman, vcov = ~ countries_gwid, stars = TRUE)
summary(model_cederman)

```
## model for selfrule as a whole
```{r}
eprrai_all <- eprrai_max

eprrai_aut <- filter(eprrai_max, regaut == 1)

model_selfrule_all <- glm(onset_do_terr_flag ~
                            selfrule_diff +
                            ethnicselfrule +
                            postwar +
                            postwar:selfrule_diff +
                            lpop +
                            lgdp +
                            ongoing +
                            peaceyears +
                            log(groupsize),
                          data = eprrai_all,
                          family = binomial(link = "logit"))
modelsummary(model_selfrule_all, statistic = "conf.int", vcov = ~ countries_gwid, stars = TRUE)

model_selfrule_aut <- glm(onset_do_terr_flag ~
                            selfrule_diff +
                            ethnicselfrule +
                            postwar +
                            postwar:selfrule_diff +
                            lpop +
                            ongoing +
                            peaceyears +
                            log(groupsize),
                      data = eprrai_aut,
                      family = binomial(link = "logit"))
modelsummary(model_selfrule_aut, vcov = ~ countries_gwid, stars = TRUE)


```

```{r}
k <- 1000

pars <- model_selfrule_all$coefficients
vcov <- sandwich::vcovCL(model_selfrule_all, cluster = ~ countries_gwid)  # clustered standard errors
model_selfrule_all.sim <- rmvnorm(k, pars, vcov)


# Relevant data
sample <- as.data.frame(model.matrix(model_selfrule_all))
span_selfrule_diff <- seq(from=range(eprrai_all$selfrule_diff)[1],to=range(eprrai_all$selfrule_diff)[2],by=1)
length_selfrule_diff <- length(span_selfrule_diff)

###########
# PRE WAR
###########
sample.pre <- subset(sample, postwar==0) 

# (1) excluded
probs_pre_excluded <- matrix(NA,k,length_selfrule_diff)
for(i in 1:k){
  model_new <- model_selfrule_all # copy model
  model_new$coefficients <- model_selfrule_all.sim[i,] # enter new coefs
  for(j in 1:length(span_selfrule_diff)){
    sample_new <- sample.pre %>% 
      mutate(selfrule_diff = span_selfrule_diff[j])
    probs_pre_excluded[i,j] <- mean(predict(model_new,
                                   newdata = sample_new %>% mutate(
                                     groupsize = exp(sample_new[,11]),
                                     status_excl = 1),
                                   type = "response"))
  }
}

# (2) included
probs_pre_included <- matrix(NA,k,length_selfrule_diff)
for(i in 1:k){
  model_new <- model_selfrule_all # copy model
  model_new$coefficients <- model_selfrule_all.sim[i,] # enter new coefs
  for(j in 1:length(span_selfrule_diff)){
    sample_new <- sample.pre %>% 
      mutate(selfrule_diff = span_selfrule_diff[j])
    probs_pre_included[i,j] <- mean(predict(model_new,
                                   newdata = sample_new %>% mutate(
                                     groupsize = exp(sample_new[,11]),
                                     status_excl = 0),
                                   type = "response"))
  }
}

# Make it tidy
probs_pre_excluded <- as_tibble(probs_pre_excluded)
colnames(probs_pre_excluded) <- span_selfrule_diff
probs_pre_excluded <- probs_pre_excluded %>% pivot_longer(cols = everything(),names_to="selfrule_diff",values_to="probability")
probs_pre_excluded <- probs_pre_excluded %>% mutate(selfrule_diff = as.numeric(selfrule_diff))

probs_pre_included <- as_tibble(probs_pre_included)
colnames(probs_pre_included) <- span_selfrule_diff
probs_pre_included <- probs_pre_included %>% pivot_longer(cols = everything(),names_to="selfrule_diff",values_to="probability")
probs_pre_included <- probs_pre_included %>% mutate(selfrule_diff = as.numeric(selfrule_diff))

# Create lower and upper limits and summarize the simulations
lower <- 0.025
higher <- 0.975
probs_pre_excluded <- probs_pre_excluded %>%
  group_by(selfrule_diff) %>% 
  summarise(mean = mean(probability),
            lo = quantile(probability,lower),
            hi = quantile(probability,higher)) %>%
  ungroup()
probs_pre_included <- probs_pre_included %>%
  group_by(selfrule_diff) %>% 
  summarise(mean = mean(probability),
            lo = quantile(probability,lower),
            hi = quantile(probability,higher)) %>%
  ungroup()

plot_pre <- ggplot(probs_pre_excluded, aes(selfrule_diff, probability))
plot_pre <- plot_pre +
  geom_line(data=probs_pre_excluded,aes(x=selfrule_diff, y=mean),col="red") +
  geom_line(data=probs_pre_excluded,aes(x=selfrule_diff, y=lo),lty=2,col="red") +
  geom_line(data=probs_pre_excluded,aes(x=selfrule_diff, y=hi),lty=2,col="red") +
  geom_line(data=probs_pre_included,aes(x=selfrule_diff, y=mean),col="blue") +
  geom_line(data=probs_pre_included,aes(x=selfrule_diff, y=lo),lty=2,col="blue") +
  geom_line(data=probs_pre_included,aes(x=selfrule_diff, y=hi),lty=2,col="blue")


############
# POST WAR
############
sample.post <- subset(sample, postwar==1) 

# (1) excluded
probs_post_excluded <- matrix(NA,k,length_selfrule_diff)
for(i in 1:k){
  model_new <- model_selfrule_all # copy model
  model_new$coefficients <- model_selfrule_all.sim[i,] # enter new coefs
  for(j in 1:length(span_selfrule_diff)){
    sample_new <- sample.post %>% 
      mutate(selfrule_diff = span_selfrule_diff[j])
    probs_post_excluded[i,j] <- mean(predict(model_new,
                                   newdata = sample_new %>% mutate(
                                     groupsize = exp(sample_new[,11]),
                                     status_excl = 1),
                                   type = "response"))
  }
}

# (2) included
probs_post_included <- matrix(NA,k,length_selfrule_diff)
for(i in 1:k){
  model_new <- model_selfrule_all # copy model
  model_new$coefficients <- model_selfrule_all.sim[i,] # enter new coefs
  for(j in 1:length(span_selfrule_diff)){
    sample_new <- sample.post %>% 
      mutate(selfrule_diff = span_selfrule_diff[j])
    probs_post_included[i,j] <- mean(predict(model_new,
                                   newdata = sample_new %>% mutate(
                                     groupsize = exp(sample_new[,11]),
                                     status_excl = 0),
                                   type = "response"))
  }
}

# Make it tidy
probs_post_excluded <- as_tibble(probs_post_excluded)
colnames(probs_post_excluded) <- span_selfrule_diff
probs_post_excluded <- probs_post_excluded %>% pivot_longer(cols = everything(),names_to="selfrule_diff",values_to="probability")
probs_post_excluded <- probs_post_excluded %>% mutate(selfrule_diff = as.numeric(selfrule_diff))

probs_post_included <- as_tibble(probs_post_included)
colnames(probs_post_included) <- span_selfrule_diff
probs_post_included <- probs_post_included %>% pivot_longer(cols = everything(),names_to="selfrule_diff",values_to="probability")
probs_post_included <- probs_post_included %>% mutate(selfrule_diff = as.numeric(selfrule_diff))

# Create lower and upper limits and summarize the simulations
lower <- 0.025
higher <- 0.975
probs_post_excluded <- probs_post_excluded %>%
  group_by(selfrule_diff) %>% 
  summarise(mean = mean(probability),
            lo = quantile(probability,lower),
            hi = quantile(probability,higher)) %>%
  ungroup()
probs_post_included <- probs_post_included %>%
  group_by(selfrule_diff) %>% 
  summarise(mean = mean(probability),
            lo = quantile(probability,lower),
            hi = quantile(probability,higher)) %>%
  ungroup()

plot_post <- ggplot(probs_post_excluded, aes(selfrule_diff, probability))
plot_post <- plot_post +
  geom_line(data=probs_post_excluded,aes(x=selfrule_diff, y=mean),col="red") +
  geom_line(data=probs_post_excluded,aes(x=selfrule_diff, y=lo),lty=2,col="red") +
  geom_line(data=probs_post_excluded,aes(x=selfrule_diff, y=hi),lty=2,col="red") +
  geom_line(data=probs_post_included,aes(x=selfrule_diff, y=mean),col="blue") +
  geom_line(data=probs_post_included,aes(x=selfrule_diff, y=lo),lty=2,col="blue") +
  geom_line(data=probs_post_included,aes(x=selfrule_diff, y=hi),lty=2,col="blue")

```


## Model for symmetric autonomy
```{r}
model_clogit <- clogit(onset_do_terr_flag ~
                         asym_low +
                         asym_same +
                         asym_high +
                         strata(countries_gwid),
                       data = eprrai_max)

 summary(model_clogit)

model_full <- glm(onset_do_terr_flag ~
                    asym_low +
                    asym_same +
                    asym_high +
                    status_egip +
                    postwar +
                    groupsize +
                    excl_groups_count +
                    lpop +
                    ongoing +
                    peaceyears +
                    asym_low:postwar +
                    asym_same:postwar +
                    asym_high:postwar,
                  data = eprrai_max,
                  family = binomial(link = "logit")
                  )


modelsummary(model_full, statistic = "{std.error}", vcov = ~ countries_gwid, stars = TRUE)

```

## Focus on the absolute degree in each area of regeional autonomy
```{r}
model_abs <- glm(onset_do_terr_flag ~
                    instdepth +
                    fiscalautonomy +
                    representation +
                    policyautonomy +
                    instdepth:regaut +
                    fiscalautonomy:regaut +
                    representation:regaut +
                    policyautonomy:regaut +
                    instdepth:regaut:postwar +
                    fiscalautonomy:regaut:postwar +
                    representation:regaut:postwar +
                    policyautonomy:regaut:postwar +
                    regaut +
                    regaut:postwar +
                    status_egip +
                    postwar +
                    groupsize +
                    ongoing +
                    lpop +
                    lgdp +
                    excl_groups_count,
                  data = eprrai_max,
                  family = binomial(link = "logit"))
modelsummary(model_abs,
             statistic = "{std.error} ",
             vcov = ~ countries_gwid, 
             stars = TRUE)
```
## Focus on the difference in degree of each authority
```{r}
model_diff <- glm(onset_do_terr_flag ~
                    instdepth_diff +
                    fiscalautonomy_diff +
                    representation_diff +
                    policyautonomy_diff +
                    instdepth_diff:regaut +
                    fiscalautonomy_diff:regaut +
                    representation_diff:regaut +
                    policyautonomy_diff:regaut +
                    instdepth_diff:regaut:postwar +
                    fiscalautonomy_diff:regaut:postwar +
                    representation_diff:regaut:postwar +
                    policyautonomy_diff:regaut:postwar +
                    regaut +
                    regaut:postwar +
                    status_egip +
                    postwar +
                    groupsize +
                    ongoing +
                    lpop +
                    lgdp +
                    excl_groups_count,
                  data = eprrai_max,
                  family = binomial(link = "logit"))
modelsummary(model_diff,
             statistic = "{std.error} ",
             vcov = ~ countries_gwid, 
             stars = TRUE)
```


## Focus on the absolute degree of regional authority, putting principal components
```{r}
eprrai_max.pca <- princomp(eprrai_max[,c(25:27,29)], cor = TRUE)
eprrai_max.pca$loadings
eprrai_max$pca_moreall <- eprrai_max.pca$scores[,1]
eprrai_max$pca_lessfiscal <- eprrai_max.pca$scores[,2]
eprrai_max$pca_lessrep <- eprrai_max.pca$scores[,3]
eprrai_max$pca_lesspolicy <- eprrai_max.pca$scores[,4]

model_diff_pca <- glm(onset_do_terr_flag ~
                    pca_moreall +
                    pca_lessfiscal +
                    pca_lessrep +
                    pca_lesspolicy +
                    pca_moreall:regaut +
                    pca_lessfiscal:regaut +
                    pca_lessrep:regaut +
                    pca_lesspolicy:regaut +
                    pca_moreall:regaut:postwar +
                    pca_lessfiscal:regaut:postwar +
                    pca_lessrep:regaut:postwar +
                    pca_lesspolicy:regaut:postwar +
                    regaut +
                    regaut:postwar +
                    status_egip +
                    postwar +
                    groupsize +
                    ongoing +
                    lpop +
                    lgdp +
                    excl_groups_count,
                  data = eprrai_max,
                  family = binomial(link = "logit"))
modelsummary(model_diff_pca,
             statistic = "{std.error} [{conf.low}, {conf.high}]",
             vcov = ~ countries_gwid, 
             stars = TRUE)
```

## Focus on the relative deprivation
```{r}
options(max.print = 1000)
table(eprrai_all$political_diff, eprrai_all$fiscal_diff)

eprrai_all.pca <- princomp(eprrai_all[,c(42,43,45,46)], cor = TRUE)
summary(eprrai_all.pca)
eprrai_all.pca$loadings

eprrai_all$pca_allenhanced <- eprrai_all.pca$scores[,1]
eprrai_all$pca_lowfiscal_highrep <- eprrai_all.pca$scores[,2]
eprrai_all$pca_highinst_lowrep <- eprrai_all.pca$scores[,3]
eprrai_all$pca_lowpolicy <- eprrai_all.pca$scores[,4]


model_reldep_all <- glm(onset_do_terr_flag ~
                        status_egip +
                        regaut +
                        postwar +
                        groupsize +
                        ongoing +
                        lpop +
                        regaut:pca_allenhanced +
                        regaut:pca_lowfiscal_highrep +
                        regaut:pca_highinst_lowrep +
                        regaut:pca_lowpolicy +
                        regaut:postwar:pca_allenhanced +
                        regaut:postwar:pca_lowfiscal_highrep +
                        regaut:postwar:pca_highinst_lowrep +
                        regaut:postwar:pca_lowpolicy  ,
                      data = eprrai_all,
                      family = binomial(link = "logit"))
modelsummary(model_reldep_all, vcov = ~ countries_gwid, stars = TRUE)
```


### Focus on the groups with autonomy
```{r}

table(eprrai_aut$political_diff, eprrai_aut$fiscal_diff)

## relative
eprrai_aut.pca <- princomp(eprrai_aut[,c(42,43,45,46)], cor = TRUE)
summary(eprrai_aut.pca)
eprrai_aut.pca$loadings

eprrai_aut$pca_allenhanced <- eprrai_aut.pca$scores[,1]
eprrai_aut$pca_lowfiscal_highrep <- eprrai_aut.pca$scores[,2]
eprrai_aut$pca_highinst <- eprrai_aut.pca$scores[,3]
eprrai_aut$pca_lowpolicy <- eprrai_aut.pca$scores[,4]

## absolute
eprrai_aut_abs.pca <- princomp(eprrai_aut[,c(25:27,29)], cor = TRUE)
eprrai_aut_abs.pca$loadings
eprrai_aut$pca_moreall <- eprrai_aut_abs.pca$scores[,1]
eprrai_aut$pca_lessfiscal <- eprrai_aut_abs.pca$scores[,2]
eprrai_aut$pca_moreinst_lessrep <- eprrai_aut_abs.pca$scores[,3]
eprrai_aut$pca_lesspolicy <- eprrai_aut_abs.pca$scores[,4]

```

```{r}
model_abs_aut <- glm(onset_do_terr_flag ~
                    pca_moreall +
                    pca_lessfiscal +
                    pca_moreinst_lessrep +
                    pca_lesspolicy +
                    pca_moreall:postwar +
                    pca_lessfiscal:postwar +
                    pca_moreinst_lessrep:postwar +
                    pca_lesspolicy:postwar +
                    status_egip +
                    postwar +
                    groupsize +
                    ongoing +
                    lpop +
                    excl_groups_count,
                  data = eprrai_aut,
                  family = binomial(link = "logit"))
modelsummary(model_abs_aut,
             vcov = ~ countries_gwid, 
             stars = TRUE)

model_reldep_aut <- glm(onset_do_terr_flag ~
                        status_egip +
                        postwar +
                        groupsize +
                        ongoing +
                        lpop +
                        pca_allenhanced +
                        pca_lowfiscal_highrep +
                        pca_highinst +
                        pca_lowpolicy +
                        postwar:pca_allenhanced +
                        postwar:pca_lowfiscal_highrep +
                        postwar:pca_highinst +
                        postwar:pca_lowpolicy,
                      data = eprrai_aut,
                      family = binomial(link = "logit"))
modelsummary(model_reldep_aut, 
             vcov = ~ countries_gwid, 
             stars = TRUE)

```




